### 2022-02-15 ms_body/manuscript.Rmd
Update Abstract
Add acknowledgements and minor edits from FI

---
output:
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    latex_engine: pdflatex
    template: "./_ms_template/svm-latex-ms.tex"
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{hyperref}
- \setlength\parindent{24pt}
- \usepackage{multirow}
- \usepackage{helvet}
- \usepackage{setspace}
- \renewcommand\familydefault{\sfdefault}
biblio-style: apsr
geometry: margin=1in
fontfamily: mathpazo
bibliography: "./ref_list/refs.bib"
csl: "./ref_list/biological-control.csl"
fontsize: 12pt
spacing: double
indent: yes
endnote: no
include-before: '`\newpage{}`{=latex}'
---

@@

Ecological models are important tools to support and guide the development and implementation of environmental policies and management programs. Species distributions models (SDM's), such as the popular MaxEnt software, are frequently used to guide conservation programmes, predict the potential distribution of invasive species, forecast the impacts of climate change and develop applied ecological research (e.g. biological control). Many applications of these models require that SDM's are transferred in either space and/or time. However, few studies to date have tested the transferability, and thus usefulness, of MaxEnt models using fully independent data. Moreover, numerous authors have raised concerns over how model complexity (controlled primarily by feature class and regularisation multiplier settings) may affect MaxEnt model transferability. In this paper, we evaluated the usefulness of MaxEnt models transferred in space using a native Australian insect, *Dasineura rubiformis* Kolesik (Diptera: Cecidomyiidae) that has been intentionally introduced as a biological control agent of the invasive plant, *Acacia mearnsii* De Wild (Fabaceae) in South Africa. MaxEnt models were developed using native-range records only (Australia) and projected over South Africa to identify the potential climatic suitability for the insect, using a range of model settings configurations. Model transferability was assessed using independent post-release data from South Africa. Our results demonstrated that MaxEnt scores were positively correlated with increased establishment rates for *D. rubiformis* in South Africa. MaxEnt model outputs and projections were relatively consistent, irrespective of the settings used. Despite MaxEnt having to extrapolate over much of South Africa, MaxEnt performance was higher than modelling climatic suitability as a function of whether models were in extrapolation or interpolation. Our study demonstrates that MaxEnt models can prove useful when transferred in space, however, users need to be aware of the effect of different model settings configurations and model extrapolation can have on model transferability and usefulness in applied ecological settings.

@@

In this study, we performed a retrospective assessment of the transferability of SDM’s built using MaxEnt [@Phillips2017]. Here, we modelled the potential climatic suitability of an insect that is native to Australia, and that has been introduced into South Africa as a biological control agent. The insect, *Dasineura rubiformis* Kolesik (Diptera: Cecidomyiidae) was introduced into South Africa from Australia in 2013, to curb the spread of the invasive Australian *Acacia mearnsii* De Wild [@Impson2013]. Extensive field surveys have been performed in Australia (characterizing the native distribution of *D. rubiformis*) [@Adair2004] and long-term post-release monitoring has been performed in South Africa to measure establishment rates of the insect, following experimental releases of the insect (Impson et al., 2021). As such, the availability of independent testing data from a separate continent to the data used to generate the models makes this an ideal study system for assessing the transferability of SDM’s.

@@

Several authors have raised concerns over the use of correlative SDM's, such as MaxEnt, when projected into new geographic regions or time periods due to issues with extrapolation into novel/non-analogous climate [@Elith2009; @Elith2011; @Yates2018]. To address these concerns, Multivariate environmental similarity surfaces (hereafter ‘MESS’) [@Elith2010] were computed to assess whether MaxEnt models were extrapolating or interpolating. MESS analyses measure the similarity of any given point to a set of reference points [reference points were defined as only the species presence points used to calibrate models following @Kriticos2014]. Negative MESS values indicate geographic regions outside the range of climate variables used to calibrate the model (i.e. extrapolation space or MESS-), while MESS values between 0 and 100 indicate geographic regions inside the range of climatic variables used to calibrate the model (i.e. interpolation space or MESS+). MESS maps are used as a measure of prediction uncertainty or caution against inferences in extrapolation space [@Elith2010].

@@

Our results indicated that MaxEnt SDM's were able to provide robust estimates of climatic suitability for *D. rubiformis* in South Africa. AUC values greater than 0.75 are typically considered good fitting models (having high predictive power) [@Fielding1997]. When MaxEnt models, calibrated using native-range records for *D. rubiformis* from Australia, were projected over South Africa, they had AUC scores of 0.89 - 0.92, indicative of high power to discriminate between sites where *D. rubiformis* had established in South Africa or not. Additionally, we showed that the probability that *D. rubiformis* was recorded at a field site in South Africa increased with higher MaxEnt climatic suitability scores. This result demonstrates the usefulness of the MaxEnt SDM and that, at least for our case-study, SDM's can be transferred into novel geographic regions, and provide valuable information to guide policy making and the development of management programmes. For example, biological control programmes such as the programme in which *D. rubiformis* is used to curtail the spread of the highly invasive weed *A. mearnsii* expend many resources (time and money) to mass-rear insect populations that are then released into the field. The positive correlation between MaxEnt suitability scores and *D. rubiformis* establishment means that researchers can develop and implement mass-rearing and experimental release programmes for the insect that prioritise releasing the insect at sites that are highly climatically suitable, and thus, more likely the insect will establish viable populations. This may assist in improving the level of control over the target weed and increasing the efficiency of resources expended by increasing the chances of establishing viable insect populations.

@@

Given that the *D. rubiformis* MaxEnt models showed high predictive accuracy when transferred in space over South Africa and the statistically significant positive correlation between MaxEnt scores and *D. rubiformis* establishment, we wish to highlight how these models can be used in an applied setting. To visualise the potential geographic regions where *D. rubiformis* may establish in South Africa, we thresholded the MaxEnt map that optimised AICc where the probability of establishment was > 75% (i.e. MaxEnt score = 0.30), given in Fig. 7. The map demonstrates that the entire south and east coast regions of South Africa are climatically suitable for *D. rubiformis*. Mass-releasing and releasing weed biological control agents is a time-consuming and costly endeavor [@Hill2021]. As such, our models provide a statistically validated approach to optimising the redistribution of *D. rubiformis* in South Africa by prioritising releases at field sites where MaxEnt scores are > 0.30, and therefore where the probability of establishment was > 75%.

@@

GFS and GDM acknowledge funding from the South African Working for Water (WfW) programme of the Department of Forestry, Fisheries and the Environment: Natural Resource Management Programmes (DFFE: NRMP). Funding was also provided by the South African Research Chairs Initiative of the Department of Science and Technology and the National Research Foundation (NRF) of South Africa. Any opinions, finding, conclusions or recommendations expressed in this material are those of the authors and the NRF does not accept any liability in this regard.

>>>>

---
output:
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    latex_engine: pdflatex
    template: "./_ms_template/svm-latex-ms.tex"
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{hyperref}
- \setlength\parindent{24pt}
- \usepackage{multirow}
- \usepackage{helvet}
- \usepackage{setspace}
- \renewcommand\familydefault{\sfdefault}
- \usepackage{fullpage}
- \usepackage{pdflscape}
biblio-style: apsr
geometry: margin=1in
fontfamily: mathpazo
bibliography: "./ref_list/refs.bib"
csl: "./ref_list/biological-control.csl"
fontsize: 12pt
spacing: double
indent: yes
endnote: no
include-before: '`\newpage{}`{=latex}'
---

@@

Ecological models are important tools to support and guide the development and implementation of environmental policies and management programs. Species distributions models (SDM's), such as the popular MaxEnt software, are frequently used to guide conservation programmes, predict the potential distribution of invasive species, forecast the impacts of climate change and develop applied ecological research (e.g. biological control). Many applications of these models require that SDM's are transferred in either space and/or time. However, few studies to date have tested the transferability, and thus usefulness, of MaxEnt models using fully independent data. Moreover, numerous authors have raised concerns over how model complexity (controlled primarily by feature class and regularisation multiplier settings) may affect MaxEnt model transferability. In this paper, we evaluated the usefulness of MaxEnt models transferred in space using a native Australian insect, *Dasineura rubiformis* Kolesik (Diptera: Cecidomyiidae) that has been intentionally introduced as a biological control agent of the invasive plant, *Acacia mearnsii* De Wild (Fabaceae) in South Africa. MaxEnt models were developed using native-range records only (Australia) and projected over South Africa to identify the potential climatic suitability for the insect, using a range of model settings configurations. Model transferability was assessed using independent post-release data from South Africa. Our results demonstrated that MaxEnt scores were positively correlated with increased establishment rates for *D. rubiformis* in South Africa. MaxEnt model outputs and projections were relatively consistent, irrespective of the settings used. Despite MaxEnt having to extrapolate over much of South Africa, MaxEnt performance was higher than modelling climatic suitability as a function of whether models were in extrapolation or interpolation. Our study demonstrates that MaxEnt models can prove useful when transferred in space, however, users need to be aware of the effect of different model settings configurations and model extrapolation can have on model transferability and usefulness in applied ecological settings. We demonstrate how validating the *D. rubiformis* MaxEnt models can be used to guide the biological control of *A. mearnsii* using *D. rubiformis*.

@@

In this study, we performed a retrospective assessment of the transferability of SDM’s built using MaxEnt [@Phillips2017]. Here, we modelled the potential climatic suitability of an insect that is native to Australia, and that has been introduced into South Africa as a biological control agent. The insect, *Dasineura rubiformis* Kolesik (Diptera: Cecidomyiidae) was introduced into South Africa from Australia in 2001, and found to be established in 2006, to curb the spread of the invasive Australian *Acacia mearnsii* De Wild [@Impson2013]. Extensive field surveys have been performed in Australia (characterizing the native distribution of *D. rubiformis*) [@Adair2004] and long-term post-release monitoring has been performed in South Africa to measure establishment rates of the insect, following experimental releases of the insect (Impson et al., 2021). As such, the availability of independent testing data from a separate continent to the data used to generate the models makes this an ideal study system for assessing the transferability of SDM’s.

@@

Several authors have raised concerns over the use of correlative SDM's, such as MaxEnt, when projected into new geographic regions or time periods due to issues with extrapolation into novel/non-analogous climate [@Elith2009; @Elith2011; @Yates2018]. To address these concerns, Multivariate environmental similarity surfaces (hereafter ‘MESS’) [@Elith2010] were computed to assess whether MaxEnt models were extrapolating or interpolating. MESS analyses measure the similarity of any given point to a set of reference points (reference points were defined as only the species presence points used to calibrate models following @Kriticos2014). Negative MESS values indicate geographic regions outside the range of climate variables used to calibrate the model (i.e. extrapolation space or MESS-), while MESS values between 0 and 100 indicate geographic regions inside the range of climatic variables used to calibrate the model (i.e. interpolation space or MESS+). MESS maps are used as a measure of prediction uncertainty or caution against inferences in extrapolation space [@Elith2010].

@@

Our results indicated that MaxEnt SDM's were able to provide robust estimates of climatic suitability for *D. rubiformis* in South Africa. AUC values greater than 0.75 are typically considered good fitting models (having high predictive power) [@Fielding1997]. When MaxEnt models, calibrated using native-range records for *D. rubiformis* from Australia, were projected over South Africa, they had AUC scores of 0.89 - 0.92, indicative of high power to discriminate between sites where *D. rubiformis* had established in South Africa or not. Additionally, we showed that the probability that *D. rubiformis* was recorded at a field site in South Africa increased with higher MaxEnt climatic suitability scores. This result demonstrates the usefulness of the MaxEnt SDM and that, at least for our case-study, SDM's can be transferred into novel geographic regions, and provide valuable information to guide policy making and the development of management programmes. For example, biological control programmes such as the programme in which *D. rubiformis* is used to curtail the spread of the highly invasive weed *A. mearnsii* expend many resources (time and money) to develop effective biological control agents. The positive correlation between MaxEnt suitability scores and *D. rubiformis* establishment means that researchers can develop experimental release programmes that prioritise releasing the insect at sites that are highly climatically suitable, and thus, more likely the insect will establish viable populations. This may assist in improving the level of control over the target weed and increasing the efficiency of resources expended by increasing the chances of establishing viable insect populations.

@@

Given that the *D. rubiformis* MaxEnt models showed high predictive accuracy when transferred in space over South Africa and the statistically significant positive correlation between MaxEnt scores and *D. rubiformis* establishment, we wish to highlight how these models can be used in an applied setting. To visualise the potential geographic regions where *D. rubiformis* may establish in South Africa, we thresholded the MaxEnt map that optimised AICc where the probability of establishment was > 75% (i.e. MaxEnt score = 0.30), given in Fig. 7. The map demonstrates that the south and east coast regions of South Africa are climatically suitable for *D. rubiformis*. Mass-releasing and releasing weed biological control agents is a time-consuming and costly endeavor [@Hill2021]. As such, our models provide a statistically validated approach to optimising the redistribution of *D. rubiformis* in South Africa by prioritising releases at field sites where MaxEnt scores are > 0.30, and therefore where the probability of establishment was > 75%.

@@

GFS and GDM acknowledge funding from the South African Working for Water (WfW) programme of the Department of Forestry, Fisheries and the Environment: Natural Resource Management Programmes (DFFE: NRMP). Funding was also provided by the South African Research Chairs Initiative of the Department of Science and Technology and the National Research Foundation (NRF) of South Africa. Any opinions, finding, conclusions or recommendations expressed in this material are those of the authors and the NRF does not accept any liability in this regard. We thank Fiona Impson, Robin Adair, Catharina Kleinjan and John Hoffmann for collecting and providing the invaluable data, and Fiona Impson for advice on a previous draft of this manuscript.

### 2022-02-15 ms_body/manuscript.tex
Add acknowledgements and minor edits from FI

\usepackage{hyperref}
\setlength\parindent{24pt}
\usepackage{multirow}
\usepackage{helvet}
\usepackage{setspace}
\renewcommand\familydefault{\sfdefault}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

Ecological models are important tools to support and guide the
development and implementation of environmental policies and management
programs. Species distributions models (SDM's), such as the popular
MaxEnt software, are frequently used to guide conservation programmes,
predict the potential distribution of invasive species, forecast the
impacts of climate change and develop applied ecological research
(e.g.~biological control). Many applications of these models require
that SDM's are transferred in either space and/or time. However, few
studies to date have tested the transferability, and thus usefulness, of
MaxEnt models using fully independent data. Moreover, numerous authors
have raised concerns over how model complexity (controlled primarily by
feature class and regularisation multiplier settings) may affect MaxEnt
model transferability. In this paper, we evaluated the usefulness of
MaxEnt models transferred in space using a native Australian insect,
\emph{Dasineura rubiformis} Kolesik (Diptera: Cecidomyiidae) that has
been intentionally introduced as a biological control agent of the
invasive plant, \emph{Acacia mearnsii} De Wild (Fabaceae) in South
Africa. MaxEnt models were developed using native-range records only
(Australia) and projected over South Africa to identify the potential
climatic suitability for the insect, using a range of model settings
configurations. Model transferability was assessed using independent
post-release data from South Africa. Our results demonstrated that
MaxEnt scores were positively correlated with increased establishment
rates for \emph{D. rubiformis} in South Africa. MaxEnt model outputs and
projections were relatively consistent, irrespective of the settings
used. Despite MaxEnt having to extrapolate over much of South Africa,
MaxEnt performance was higher than modelling climatic suitability as a
function of whether models were in extrapolation or interpolation. Our
study demonstrates that MaxEnt models can prove useful when transferred
in space, however, users need to be aware of the effect of different
model settings configurations and model extrapolation can have on model
transferability and usefulness in applied ecological settings.

@@

In this study, we performed a retrospective assessment of the
transferability of SDM's built using MaxEnt (Phillips et al., 2017).
Here, we modelled the potential climatic suitability of an insect that
is native to Australia, and that has been introduced into South Africa
as a biological control agent. The insect, \emph{Dasineura rubiformis}
Kolesik (Diptera: Cecidomyiidae) was introduced into South Africa from
Australia in 2013, to curb the spread of the invasive Australian
\emph{Acacia mearnsii} De Wild (Impson et al., 2013). Extensive field
surveys have been performed in Australia (characterizing the native
distribution of \emph{D. rubiformis}) (Adair, 2004) and long-term
post-release monitoring has been performed in South Africa to measure
establishment rates of the insect, following experimental releases of
the insect (Impson et al., 2021). As such, the availability of
independent testing data from a separate continent to the data used to
generate the models makes this an ideal study system for assessing the
transferability of SDM's.

@@

Several authors have raised concerns over the use of correlative SDM's,
such as MaxEnt, when projected into new geographic regions or time
periods due to issues with extrapolation into novel/non-analogous
climate (Elith et al., 2011; Elith and Leathwick, 2009; Yates et al.,
2018). To address these concerns, Multivariate environmental similarity
surfaces (hereafter `MESS') (Elith et al., 2010) were computed to assess
whether MaxEnt models were extrapolating or interpolating. MESS analyses
measure the similarity of any given point to a set of reference points
(reference points were defined as only the species presence points used
to calibrate models following Kriticos et al., 2014). Negative MESS
values indicate geographic regions outside the range of climate
variables used to calibrate the model (i.e.~extrapolation space or
MESS-), while MESS values between 0 and 100 indicate geographic regions
inside the range of climatic variables used to calibrate the model
(i.e.~interpolation space or MESS+). MESS maps are used as a measure of
prediction uncertainty or caution against inferences in extrapolation
space (Elith et al., 2010).

@@

Our results indicated that MaxEnt SDM's were able to provide robust
estimates of climatic suitability for \emph{D. rubiformis} in South
Africa. AUC values greater than 0.75 are typically considered good
fitting models (having high predictive power) (Fielding and Bell, 1997).
When MaxEnt models, calibrated using native-range records for \emph{D.
rubiformis} from Australia, were projected over South Africa, they had
AUC scores of 0.89 - 0.92, indicative of high power to discriminate
between sites where \emph{D. rubiformis} had established in South Africa
or not. Additionally, we showed that the probability that \emph{D.
rubiformis} was recorded at a field site in South Africa increased with
higher MaxEnt climatic suitability scores. This result demonstrates the
usefulness of the MaxEnt SDM and that, at least for our case-study,
SDM's can be transferred into novel geographic regions, and provide
valuable information to guide policy making and the development of
management programmes. For example, biological control programmes such
as the programme in which \emph{D. rubiformis} is used to curtail the
spread of the highly invasive weed \emph{A. mearnsii} expend many
resources (time and money) to mass-rear insect populations that are then
released into the field. The positive correlation between MaxEnt
suitability scores and \emph{D. rubiformis} establishment means that
researchers can develop and implement mass-rearing and experimental
release programmes for the insect that prioritise releasing the insect
at sites that are highly climatically suitable, and thus, more likely
the insect will establish viable populations. This may assist in
improving the level of control over the target weed and increasing the
efficiency of resources expended by increasing the chances of
establishing viable insect populations.

@@

Given that the \emph{D. rubiformis} MaxEnt models showed high predictive
accuracy when transferred in space over South Africa and the
statistically significant positive correlation between MaxEnt scores and
\emph{D. rubiformis} establishment, we wish to highlight how these
models can be used in an applied setting. To visualise the potential
geographic regions where \emph{D. rubiformis} may establish in South
Africa, we thresholded the MaxEnt map that optimised AICc where the
probability of establishment was \textgreater{} 75\% (i.e.~MaxEnt score
= 0.30), given in Fig. 7. The map demonstrates that the entire south and
east coast regions of South Africa are climatically suitable for
\emph{D. rubiformis}. Mass-releasing and releasing weed biological
control agents is a time-consuming and costly endeavor (Hill et al.,
2021). As such, our models provide a statistically validated approach to
optimising the redistribution of \emph{D. rubiformis} in South Africa by
prioritising releases at field sites where MaxEnt scores are
\textgreater{} 0.30, and therefore where the probability of
establishment was \textgreater{} 75\%.

>>>>

\usepackage{hyperref}
\setlength\parindent{24pt}
\usepackage{multirow}
\usepackage{helvet}
\usepackage{setspace}
\renewcommand\familydefault{\sfdefault}
\usepackage{fullpage}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

Ecological models are important tools to support and guide the
development and implementation of environmental policies and management
programs. Species distributions models (SDM's), such as the popular
MaxEnt software, are frequently used to guide conservation programmes,
predict the potential distribution of invasive species, forecast the
impacts of climate change and develop applied ecological research
(e.g.~biological control). Many applications of these models require
that SDM's are transferred in either space and/or time. However, few
studies to date have tested the transferability, and thus usefulness, of
MaxEnt models using fully independent data. Moreover, numerous authors
have raised concerns over how model complexity (controlled primarily by
feature class and regularisation multiplier settings) may affect MaxEnt
model transferability. In this paper, we evaluated the usefulness of
MaxEnt models transferred in space using a native Australian insect,
\emph{Dasineura rubiformis} Kolesik (Diptera: Cecidomyiidae) that has
been intentionally introduced as a biological control agent of the
invasive plant, \emph{Acacia mearnsii} De Wild (Fabaceae) in South
Africa. MaxEnt models were developed using native-range records only
(Australia) and projected over South Africa to identify the potential
climatic suitability for the insect, using a range of model settings
configurations. Model transferability was assessed using independent
post-release data from South Africa. Our results demonstrated that
MaxEnt scores were positively correlated with increased establishment
rates for \emph{D. rubiformis} in South Africa. MaxEnt model outputs and
projections were relatively consistent, irrespective of the settings
used. Despite MaxEnt having to extrapolate over much of South Africa,
MaxEnt performance was higher than modelling climatic suitability as a
function of whether models were in extrapolation or interpolation. Our
study demonstrates that MaxEnt models can prove useful when transferred
in space, however, users need to be aware of the effect of different
model settings configurations and model extrapolation can have on model
transferability and usefulness in applied ecological settings. We
demonstrate how validating the \emph{D. rubiformis} MaxEnt models can be
used to guide the biological control of \emph{A. mearnsii} using
\emph{D. rubiformis}.

@@

In this study, we performed a retrospective assessment of the
transferability of SDM's built using MaxEnt (Phillips et al., 2017).
Here, we modelled the potential climatic suitability of an insect that
is native to Australia, and that has been introduced into South Africa
as a biological control agent. The insect, \emph{Dasineura rubiformis}
Kolesik (Diptera: Cecidomyiidae) was introduced into South Africa from
Australia in 2001, and found to be established in 2006, to curb the
spread of the invasive Australian \emph{Acacia mearnsii} De Wild (Impson
et al., 2013). Extensive field surveys have been performed in Australia
(characterizing the native distribution of \emph{D. rubiformis}) (Adair,
2004) and long-term post-release monitoring has been performed in South
Africa to measure establishment rates of the insect, following
experimental releases of the insect (Impson et al., 2021). As such, the
availability of independent testing data from a separate continent to
the data used to generate the models makes this an ideal study system
for assessing the transferability of SDM's.

@@

Several authors have raised concerns over the use of correlative SDM's,
such as MaxEnt, when projected into new geographic regions or time
periods due to issues with extrapolation into novel/non-analogous
climate (Elith et al., 2011; Elith and Leathwick, 2009; Yates et al.,
2018). To address these concerns, Multivariate environmental similarity
surfaces (hereafter `MESS') (Elith et al., 2010) were computed to assess
whether MaxEnt models were extrapolating or interpolating. MESS analyses
measure the similarity of any given point to a set of reference points
(reference points were defined as only the species presence points used
to calibrate models following Kriticos et al. (2014)). Negative MESS
values indicate geographic regions outside the range of climate
variables used to calibrate the model (i.e.~extrapolation space or
MESS-), while MESS values between 0 and 100 indicate geographic regions
inside the range of climatic variables used to calibrate the model
(i.e.~interpolation space or MESS+). MESS maps are used as a measure of
prediction uncertainty or caution against inferences in extrapolation
space (Elith et al., 2010).

@@

Our results indicated that MaxEnt SDM's were able to provide robust
estimates of climatic suitability for \emph{D. rubiformis} in South
Africa. AUC values greater than 0.75 are typically considered good
fitting models (having high predictive power) (Fielding and Bell, 1997).
When MaxEnt models, calibrated using native-range records for \emph{D.
rubiformis} from Australia, were projected over South Africa, they had
AUC scores of 0.89 - 0.92, indicative of high power to discriminate
between sites where \emph{D. rubiformis} had established in South Africa
or not. Additionally, we showed that the probability that \emph{D.
rubiformis} was recorded at a field site in South Africa increased with
higher MaxEnt climatic suitability scores. This result demonstrates the
usefulness of the MaxEnt SDM and that, at least for our case-study,
SDM's can be transferred into novel geographic regions, and provide
valuable information to guide policy making and the development of
management programmes. For example, biological control programmes such
as the programme in which \emph{D. rubiformis} is used to curtail the
spread of the highly invasive weed \emph{A. mearnsii} expend many
resources (time and money) to develop effective biological control
agents. The positive correlation between MaxEnt suitability scores and
\emph{D. rubiformis} establishment means that researchers can develop
experimental release programmes that prioritise releasing the insect at
sites that are highly climatically suitable, and thus, more likely the
insect will establish viable populations. This may assist in improving
the level of control over the target weed and increasing the efficiency
of resources expended by increasing the chances of establishing viable
insect populations.

@@

Given that the \emph{D. rubiformis} MaxEnt models showed high predictive
accuracy when transferred in space over South Africa and the
statistically significant positive correlation between MaxEnt scores and
\emph{D. rubiformis} establishment, we wish to highlight how these
models can be used in an applied setting. To visualise the potential
geographic regions where \emph{D. rubiformis} may establish in South
Africa, we thresholded the MaxEnt map that optimised AICc where the
probability of establishment was \textgreater{} 75\% (i.e.~MaxEnt score
= 0.30), given in Fig. 7. The map demonstrates that the south and east
coast regions of South Africa are climatically suitable for \emph{D.
rubiformis}. Mass-releasing and releasing weed biological control agents
is a time-consuming and costly endeavor (Hill et al., 2021). As such,
our models provide a statistically validated approach to optimising the
redistribution of \emph{D. rubiformis} in South Africa by prioritising
releases at field sites where MaxEnt scores are \textgreater{} 0.30, and
therefore where the probability of establishment was \textgreater{}
75\%.
